### 2019-12-14 Statistical Methods/04_probability.rmd
statistical methods, ch 4
statistical methods, ch 4
statistical methods, ch3

@@

@@

@@

@@

@@

@@

@@

@@

@@

b.) $P(Z > 1.25)$

c.) $P(-1.2 \le Z \le 1.2)$

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

```{r, echo = T}
n <- 25
p <- .4
q <- 1 - p

@@

```{r, echo = T}
pbinom(10, size = n, prob = p)
```

@@

```{r, echo = T}
pbinom(11, size = n, prob = p)
```

@@

```{r, echo = T}
pbinom(9, size = n, prob = p, lower.tail = F)
```

@@

```{r, echo = T}
pbinom(8, size = n, prob = p, lower.tail = F)
```

@@

phat <- p
v <- p*q/n
```

$\mu = `r mu`$, $\sigma^2 = `r variance`$, $\hat{p} = `r phat`$, $\sigma^2 = `r v`$

@@

```{r, echo = T}
pnorm(1.5, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(-2.5)
```

@@

```{r, echo = T}
# P(Z > -1) - P(Z > 1)
pnorm(-1, lower.tail = F) - pnorm(1, lower.tail = F)

# 1 - 2*tail_area
1 - 2 * pnorm(1, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(0.5)
```

b.) $P(Z > -1.25)$

```{r, echo = T}
pnorm(-1.25, lower.tail = F)
```

c.) $P(-1.2 < Z < 1.2)$

```{r, echo = T}
1 - 2 *pnorm(1.2, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(1.8, lower.tail = T) - pnorm(-1.8)
```

a.) $P(Z < -.5)$

```{r, echo = T}
1 - pnorm(-.5, lower.tail = F)
```

b.) $P(Z < 1.2)$

```{r, echo = T}
1 - pnorm(1.2, lower.tail = F)
```

c.) $P(Z > 2.1)$

```{r, echo = T}
pnorm(2.1, lower.tail = F)
```

d.) $P(-.28 < Z < 0.28)$

```{r, echo = T}
pnorm(-.28, lower.tail = F) - pnorm(.28, lower.tail = F)
```

If Z has a standard normal distribution, find _c_ such that:

a.) $P(Z \le c) = 0.0099$

```{r, echo = T}
qnorm(0.0099)
```

b.) $P(Z < c) = .9732$

```{r, echo = T}
qnorm(.9732)
```

c.) $P(Z > c) = 0.5691$

```{r, echo = T}
qnorm(.5691, lower.tail = F)
```

d.) $P(-c \le Z \le c) = 0.2358$

```{r, echo = T}
qnorm( (1 + 0.2358) / 2)
```

If X has a standard normal distribution with, determine:

a.) $P(Z > c) = 0.0764$

@@

b.) $P(Z > c) = 0.5040$

@@

c.) $P(-c \le Z \le c) = 0.9108$

@@

d.) $P(-c \le Z \le c) = 0.8$

@@

If X has a normal distribution with mean $\mu = 50$ and standard deviation $\sigma = 9$

a.) $P(x \le 40)$

b.) $P(X < 55)$

c.) $P(X > 60)$

d.) $P(40 \le X \le 60)$

@@

If X has a normal distribution with $\mu = 20$ and $\sigma = 9$, determine:

a.) $P(x < 22)$

b.) $P(X > 17)$

c.) $P(X > 15)$

d.) $P(2 \le X \le 38)$

@@

If X has a normal distribution with mean $\mu = .75$ and standard deviation $\sigma = 0.5$, determine:

a.) $P(0.5 < X < 1)$

b.) $P(0.25 < X < 1.25)$

@@

If X has a normal distribution, determine _c_ such that:

$P(\mu - c\sigma < X < \mu + c\sigma) = .95$

@@

If X has a normal distribution, determine _c_ such that:

$P(\mu - c\sigma < X < \mu + c\sigma) = .8$

@@

Assuming that the scores on a math achievement test are normally distributed with $\mu = 69$ and standard deviation $\sigma = 10$, what is the probability of getting a score greater than 78?

@@

In the previous problem, how high must someone score to be in the top 5%?

That is, determine _c_ such that $P(X > c) = 0.05$

@@

A manufacturer of car batteries claims that the life of their batteries is normally distributed with mean $\mu = 58$ and $\sigma = 3$.

Determien the probability that a randomly selected battery will last at least 62 months.

@@

Assume that the income of pediatricials is normally distributed with mean $\mu = \$100,000$ and $\sigma = 10,000$.

Determine the probability of observing an income between $85,000 and $115,000.

@@

Suppose the winnings of gamblers at Las Vegas are normally distributed with $\mu = -300$ and $\sigma = 100$.

Determine the probability that a gambler does not lose any money.

@@

A large computer company claims that their salaries are normally distributed with $\mu = \$50,000$ and $\sigma = \$10,000$.

What is the probability of observing an income between $40,000 and $60,000?
